An Open Platform for Managing Short Programming Exercises

### 2013-06-20 paper/paper.tex
another discussion question
a philosophical question

{\bf Given an effective mechanism for sharing curriculum materials, could
courses at a number of institutions converge towards an optimum?}
Discuss.

@@

>>>>

{\bf Given an effective mechanism for sharing curriculum materials, could
courses at a number of institutions converge towards an optimum?}
This question is more philosophical, and is based on the observation that
curricula and pedagogy vary widely between instructors and institutions,
even for the ``same'' course \cite{Hertz:2010:CCM:1734263.1734335}.  We find ourselves wondering
if more effective ways ways of sharing curriculum materials would lead
to the best materials and ideas propagating widely, and if high-quality introductory
programming courses could created as a ``mash-up'' of materials created by
many authors at many institutions.  CloudCoder and similar systems
could be one mechanism enabling this type of transfer.

@@

{\bf What is the right balance between short programming exercises and
  longer ``nifty'' assignments?}
Discuss.

{\bf What can we do to encourage students to use their time effectively outside of class?}
